---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



```{r,echo=FALSE}
library(knitr)
```
# preDose <img align="right" src = "man/figures/predose_hex_only.png" width="135px">

# preDose: An R-package for Robust External Evaluation of popPKPD Models. 

preDose is a free and open source package that automatize the process of *external evaluation process* using an independent dataset from which the original popPKPD model was developed.

Currently, the user can choose to use the package based on either[lixoftconnectors](https://monolix.lixoft.com/monolix-api/examples/)  or via [mapbayr](https://github.com/FelicienLL/mapbayr)  depending on whether lixoftconnectors(which comes with the installation of Lixoft software) is available in their environment.


You can perform an external evaluation for a single model from :

* a population PKPD model 
(coded in [mrgsolve](https://github.com/metrumresearchgroup/mrgsolve), or from [Monolix](https://monolix.lixoft.com/demo-projects/modelimplementation/),
* a data set with concentrations (NONMEM format or Monolix format)


The package requires the user to provide a popPKPD model and an external dataset, regardless of the processing engine they choose. Below are the functions established for both utilities.


## Installation

You can install the development version of preDose from [GitHub](https://github.com/) with:
```{r, eval = F}
install.packages("devtools")
devtools::install_github("Martin-Umpierrez/preDose")
```

```{r, setup, include=FALSE}
library(mapbayr)
library(mrgsolve)
```

```{r message=FALSE, include=FALSE, results='hide'}
devtools::load_all()
```

## Example

This is a basic example which shows you how to solve a common problem for external evaluation. 

```{r example}
library(preDose)
## basic example code
```

#### 1) Properly code you model 

##### 1.1) Code your model in mrgsolve format. 
This is an example of a Tacrolimus model developed by Han et al(2011) : "Prediction of the tacrolimus population pharmacokinetic parameters according to CYP3A5 genotype and clinical factors using NONMEM in adult kidney transplant recipients"

```{r Model, echo=T, message=FALSE, results='hide'}
Han_etal_test<-
  '$PROB
# One Comparment Model with first order absorption- Ka is FIXED
$GLOBAL
#define CP (CENT/iV)
$CMT  @annotated
EV   : Extravascular compartment
CENT : Central compartment#two compt model with first order absorption

$PARAM @annotated 
CL  :  24.13 : Clearance for CYP3A5*3*3
V  :  716 : central volume
KA  : 4.5 : absorption rate constant
ETA1 : 0 : IIVCl (L/h)
ETA2 : 0 : IIVV (L)

$PARAM @annotated @covariate
POD    : 0   : COV POST OPERATIVE DAY
HCT      : 0  : COV HCH
WT      : 0  : COV WT
CYP3A5      : 0  : Polimorfismo CYP3A5
OCC     : -99  : Occasion, shall be passed by dataset imported

$ODE
dxdt_EV = -iKA*EV;
dxdt_CENT = iKA*EV  - iCL*CP;

$MAIN
##CYP3A5 effect on Cl##

double HM = 1.186 ;  ####Rapid Metabolizer ####
double IM = 1.13 ;  ####Intermediate Metabolizer ####
double PM = 1 ;  ####Poor Metabolizer####

if(CYP3A5==1) double CL_EFFECT = HM ;
if(CYP3A5==2) CL_EFFECT = IM ;
if(CYP3A5==3) CL_EFFECT = PM ;

double CL_HCT1 = 1.3458 ; ##Effect of HCT< 33
double CL_HCT2 = 1.124 ;  ##Effect of HCT >33

if(HCT< 33) double CL_HCT = CL_HCT1 ;
if(HCT >= 33) CL_HCT = CL_HCT2 ;

double CL_POD = - 0.00762 ;

double iCL =  CL *exp(ETA(1) + ETA1)* pow(POD, CL_POD) * CL_EFFECT * CL_HCT ;  
double iV =  V *exp(ETA(2) + ETA2) * exp (0.355*WT/59.025) ;  
double iKA =  KA ;    


$OMEGA @name IIV 
0.248 
0.237

$SIGMA  @name SIGMA @annotated
ADD : 0 : ADD residual error
PROP : 0.16 : Proportional residual error


$TABLE
double IPRED = CENT/iV;
double DV = IPRED * (1 + PROP) ;

$CAPTURE @annotated
CP : Plasma concentration (mass/volume)
iCL :  Clearance
iV : :Central Volume
iKA : KA: absorption rate constant
EVID : EVENT ID
DV : PREDICCION
OCC: OCCASION

               '

```

#### 2) Import your external data

Import the data set either in Monolix-formatted datasets or NM-TRAN-formatted datasets
Ensure that the dataset structure aligns with the required format for proper processing.

```{r external_data_mapbayr}
data("external_data_mapbayr", package = "preDose")  # Cargar dataset desde el paquete
head(external_data_mapbayr)  # Ver primeras filas
```

#### 3) Calculate individual parameters with `run_MAP_estimations`

The `run_MAP_estimations()` function returns a list with four elements:

* **Observed data per occasion**  
  Includes the observed values for each individual in each occasion.

* **Treatments per occasion**  
  Contains information on the treatments administered in each occasion.

* **Estimated individual parameters**  
  Provides the MAP-estimated values of individual parameters for each subject and occasion.

* **Mandatory**  
  + Progressive  
  + Most_Recent_Progressive  
  + Cronologic_Ref  
  + Most_Recent_rEF





```{r map_estim, echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
map.est <- run_MAP_estimations(model_name = "Test_Model",
                               model_code = Han_etal_test,
                               tool = "mapbayr",
                               data = external_data_mapbayr,
                               evaluation_type= "Progressive")  # Cargar dataset desde el paquete
head(map.est[["map_estimations"]])

```

#### 4) Actualize  Indiviudal models with parameters calcualted before. 

```{r indiviudal_Actualization, echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
updt.md = actualize_model(map.est, evaluation_type = "Progressive") #### Individual Models
```

#### 5) Simulate observed concentrations

```{r Simulate, echo=TRUE, message=FALSE, warning=FALSE, error=FALSE, cache=TRUE }
sim = run_ind_simulations(updt.md, map.est) # Simulate for every ID in every OCC

```

#### 6) Calucalte Metrics Accross Occasions 

```{r calcualte_metrics, echo=TRUE, message=FALSE, cache=TRUE}
metrics = metrics_occ(simulations= sim, 
                      tool="mapbayr") # Simulate for every ID in every OCC

head((metrics[["metrics"]]),10)

head(metrics[2])

```

#### 7) Make Some Important Plots to compare metrics
##### 7.1) Bias BarPlot 
```{r plot1, echo=TRUE, message=FALSE}

plot1 = metrics_Plot(mm=metrics,
             type = "bias_barplot")

print(plot1)

```
##### 7.2) Bias boxplot 

```{r plot2, echo=TRUE, message=FALSE}

plot2 = metrics_Plot(mm=metrics,
             type = "bias_boxplot")

print(plot2)

```

##### 7.3) Bias dotplot 

```{r plot3, echo=TRUE, message=FALSE}

plot3 = metrics_Plot(mm=metrics,
             type = 'bias_dotplot')

print(plot3)

```

#### 8) Import Models and assess the predicitve performance
##### 8.1) New Models and Estimations

```{r new_scenarios, echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE}

source("inst/model_examples/ZuoX_etal_2013.R")

map.est.2 <- run_MAP_estimations(model_name = "Test_Model2",
                               model_code = ZuoX_etalfull_noCYP3A4,
                               tool = "mapbayr",
                               data = external_data_mapbayr,
                               evaluation_type= "Progressive") 

updt.md2 = actualize_model(map.est.2, evaluation_type = "Progressive")

sim2 = run_ind_simulations(updt.md2, map.est.2)

metrics2 = metrics_occ(simulations= sim2, 
                      tool="mapbayr") 

```

##### 8.2) Compare Models
###### 8.2.1) By Plotting: 
First Combine all metrics for all the tested models
```{r plot_comparisson, echo=TRUE, message=FALSE, warning=TRUE, cache=TRUE}
metrics2 = metrics_occ(simulations= sim2, 
                      tool="mapbayr") # Simulate for every ID in every OCC

###### Generate a summary of metrics for all tested models
model_list <- list(list(model_name="Han_etal", metrics_list=metrics),
                   list(model_name="Zuo_etal", metrics_list=metrics2))

#### Use combine_metrics() function with the summary created
combined_results<- combine_metrics(model_list)

#### Make the Plot! 
plot_comparrison <- plot_combined(combined_results,
                                  'bias_barplot')

print(plot_comparrison)

```


###### 8.2.2) Select models according to a specific evaluation metric and threshold using select_best_models() function
The `select_best_models()` function

```{r model_selection, echo=TRUE, message=FALSE, warning=TRUE, cache=TRUE}

Best_fit <- select_best_models(combined_results, metric = "rBIAS",
                               top_n = 1)

print(Best_fit)

```









