---
title: "Computing Metrics by OCC"
author: "Martin Umpierrez"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Computing Metrics by Occasion}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(preDose)
```

## Introduction

This vignette demonstrates how to use the `metrics_occ` function to compute main prediction error metrics to assess the predictive performance of each popPK model grouped by occasion (OCC).

## Function Overview

The `metrics_occ` function processes simulation outputs from either `mapbayr` or `lixoftConnectors` and returns summary metrics for each occasion.

### Required Inputs
- `simulations`: A list from `run_ind_simulations()` (for `mapbayr`).
- `sims`: A list of outputs from `lixoftConnectors`.
- `tool`: A string indicating the tool used (`"mapbayr"` or `"lixoftConnectors"`).


## Example Usage

```{r example, eval=FALSE}
# Load necessary data
simulations <- run_ind_simulations()

# Compute metrics using mapbayr
results <- metrics_occ(simulations = simulations, tool = "mapbayr")

# Accessing results
metrics_summary <- results$metrics_means
```

## Interpretation of Results

- `metrics`: Contains individual predictions, observations, and error metrics per occasion.
- `metrics_means`: Provides summary statistics, including rBIAS, MAPE, rRMSE, IF20, and IF30.

## Additional Information

For more details, see `?metrics_occ` in R.

