---
title: "actualize_model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{actualize_model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(preDose)
```

## Introduction

This vignette demonstrates how to use the `actualize_model` function to obtain each individual model to perform simulations in every Occasion (OCC)

## Function Overview

The `actualize_model` function processes the element from the function `run_MAP_estimation` containing MAP estiamtions and an evaluation type. Returns a single model for every ID in each Occasion

### Required Inputs
- `actualization_map`: A list from `run_MAP_estimations()` containing the posterior distribution
- `evaluation_type`: A character vector with the type of evaluation. it must be the same used in `run_MAP_estimations()`. Options included:
  - "Progressive"
  - "Most_Recent_Progressive"
  - "Cronologic_Ref"
  - "Most_Recent_Ref"

## Running the Function 

```{r, eval=FALSE}
# Load necessary data (assume precomputed objects)
individual_models <- actualize_model(MAP_estimations,
                                     evaluation_type="Progressive")
```

## Conclusion

The `actualize_model` function provides a flexible framework for updating MAP estimations dynamically across occasions. This is particularly useful in population pharmacokinetics where models evolve based on new patient data.

## Interpretation of Results

- `ind_model`: A list containing the actualized individual model with the posterior distribution for each occasion and ID
- `eval_type`: Contains a string with the evaluation type utilized

## Additional Information

For more details, see `?actualize_model` in R.
