---
title: "combine_metrics"
author: "Martin Umpierrez"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{combine_metrics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(preDose)
```


## Introduction

This vignette demonstrates how to implement the `combine_metrics` function to merge different metrics coming from different models when users want to compare them. 

## Required Inputs

The function requires one main inputs:
- `models`: A list of list: Every List contains the name of a Model(i.e " Model_1" and the resulting metrics generated from `metrics_occ`


## Example Usage

```{r example, eval=TRUE}
# Load necessary data (assume precomputed objects)
set.seed(123)
generate_fake_metrics <- function(n_occasions = 3) {
  data.frame(
    OCC = rep(1:n_occasions),  # Simula varias ocasiones
    rBIAS = rnorm(n_occasions, mean = 0, sd = 10), 
    rBIAS_lower = rnorm(n_occasions, mean = -5, sd = 5), 
    rBIAS_upper = rnorm(n_occasions, mean = 5, sd = 5), 
    MAIPE = runif(n_occasions, min = 10, max = 50), 
    IF20 = runif(n_occasions, min = 20, max = 80), 
    IF30 = runif(n_occasions, min = 30, max = 90)
  )
}

# Fake Simulation of metrics to use the model
results1 <- list(metrics_means = generate_fake_metrics())
results2 <- list(metrics_means = generate_fake_metrics())

# List of Models containing:  Name of Models and the metrics results
models_list <- list(
  list(model_name = "Test_Model1", metrics_list = results1),
  list(model_name = "Test_Model2", metrics_list = results2)
)

# Use the combine_metrics() function
combined_results <- combine_metrics(models_list)

# Visualize the metrics in the same data.frame
print(combined_results)

```
