---
title: "Running Individual Simulations"
author: "Martin Umpierrez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{run_ind_simulations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(preDose)
```

## Introduction

This vignette demonstrates how to use the `run_ind_simulations` function to simulate individual drug concentrations based on posterior estimations and treatment schedules.

## Required Inputs

The function requires two main inputs:
- `individual_model`: A list generated from `actualize_model`, containing posterior estimations.
- `tto_occ`: A list generated from `run_map_estimations`, containing treatment schedules.

## Example Usage

```{r example, eval=FALSE}
# Load necessary data (assume precomputed objects)
individual_model <- actualize_model()
tto_occ <- run_map_estimations()

# Run the individual simulations
results <- run_ind_simulations(individual_model, tto_occ)

# Accessing results
sim_results <- results$simulation_results
treatments <- results$ttoocc
events <- results$events_tto
```

## Interpretation of Results

- `simulation_results`: Contains simulated drug concentrations for each occasion and individual.
- `ttoocc`: Stores treatment information organized by occasion.
- `events_tto`: Lists treatment events for each occasion.

## Additional Information

For more details, see `?run_ind_simulations` in R.

---

To include this vignette in your package, rebuild the documentation:

```r
devtools::build_vignettes()
